Brownian Dynein Model

### 2015-07-22 latex/derivation.tex
slightly clean up last equation.

$$
\hspace*{-4cm} \dot{\Theta}_{mr} =
$$
$$
\hspace*{-7cm} \frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
{L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
$$

>>>>

\begin{align}
\dot{\Theta}_{mr} &= \nonumber \\
&\frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
{L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
\end{align}
